\Large \bf Lissy: Experimenting with on-chain order books

### 2022-06-02 LaTeX-LNCS-2022/sections/paper.tex
preparing for wtsc

We assume the reader is familiar with the following concepts: blockchain technology; smart contracts and decentralized applications (DApps) on Ethereum; how Ethereum transactions are structured, broadcast, and finalized; the gas model including the gas limit (approximately 11M gwei at the time of our experiments) per block. A \textbf{gas refund} is a more esoteric subject (not covered thoroughly in any academic work to our knowledge) that we use heavily in our optimizations. Briefly, certain EVM operations (\texttt{SELFDESTRUCT} and \texttt{SSTORE 0}) cost negative gas, with the follow caveats: the refund is capped at 50\% of the total gas cost of the transaction, and (2) the block gas limit applies to the pre-refunded amount (\ie a transaction receiving a full refund can cost up to 5.5M gas with an 11M limit). We provide full details of all of these topics in Appendix~\ref{app:ethback}.

@@

Table~\ref{tab:eval2} illustrates various trade execution systems and summarizes their advantages and disadvantages. Appendix~\ref{app:markets} provides a full justification for the table. Briefly, fully decentralized, on-chain exchanges require the lowest trust, provide instant settlement, and have transparent trading rules that will always execute correctly. Front-running attacks (see Section~\ref{sec:front} for a very thorough discussion) are weaknesses inherent in blockchains that require specific mitigation.

@@

A call market opens for traders to submit bids and asks which are enqueued until the market closes. Trades are executed by matching the best priced bid to the best priced ask until the best bid is less than the best ask, then all remaining trades are discarded. See Appendix~\ref{app:cm} for a numeric example. If Alice's bid of \$100 is executed against Bob's ask of \$90, Alice pays \$100, Bob receives \$90 and the \$10 difference (called a price improvement) is given to miners for reasons in explained in the front-running evaluation (Section~\ref{sec:front}).

@@

\item \textbf{Heap with Mapping.} In this variant, we store a key for the order in the heap instead of the entire order itself. Once a key is dequeued, the order struct is drawn from a Solidity mapping (which stores key-value pairs very efficiently). This is asymptotically the same and faster with variable-sized data.

@@

The lesson here is that gas refunds incentivize developers to clean up storage variables they will not use again, but it is highly contextual as to whether it will pay for itself. Further, the cap on the maximum refund means that refunds are not fully received for large cleanup operations (however removing the cap impacts the miners' incentives to include the transaction).  In Appendix~\ref{app:clean}, we present a second case study of the cost-benefit of clearing a mapping when it is no longer needed (including our idea to store the mapping in its own contract so it can \texttt{SELFDESTRUCT} with a single function call). The unfortunate takeaway is, again, that it is cheapest to leave the mapping in place. Cleaning up EVM state is a complicated and under-explored area of Ethereum in the research literature. For our own work, we strive to be good citizens of Ethereum and clean up to the extent that we can---thus all PQs in Table~\ref{tab:PQUnitTests} implement some cleanup.

@@

\textit{Layer 2 (L2)} solutions~\cite{gudgeon2020sok} are a group of scaling technologies proposed to address specific drawbacks of executing transactions on Ethereum, which is considered \textit{Layer 1 (L1)}. Among these proposals, \textit{roll-ups} prioritize reducing gas costs (as opposed to other valid concerns like latency and throughput, which are secondary for \cm). We review two variants, \textit{optimistic roll-ups} and \textit{zk roll-ups}, in Appendix~\ref{app:rollup}. Briefly, in a roll-up, every transaction is stored (but not executed) on Ethereum, then executed off-chain, and the independently verifiable result is pushed back to Ethereum, with some evidence of being executed correctly. In the Appendix, we also compare \cm on Arbitrum to Loopring 3.0.

@@

In our \cm variant on Arbitrum, the validators do all computations (both enqueuing and dequeuing) so we choose to use a heap with dynamic array for our priority queue, which balances the expense of both operations. Heaps are 32\% more efficient than linked lists for submitting orders and 29\% less efficient for closing. Recall that without a roll-up, such a priority queue can only match 38 pairs at a cost of 5,372,679 gas. Table~\ref{tab:arbitrum_performance} shows that 38 pairs cost only 6,569 in L1 gas (a 99.88\% savings). This is the cost of submitting the \texttt{closeMarket()} transaction to the Inbox to be recorded, which is 103 bytes of calldata. Most importantly, recording \texttt{closeMarket()} in the Inbox will always cost around 6,569 even as the number of trades increases from 38 pairs to thousands or millions of pairs. Of course, as the number of trades increase, the work for the validators on L2 increases, as measured in ArbGas. The price of ArbGas in Gwei is not well established but is anticipated to be relatively cheap.  Arbitrum also reduces the costs for traders to submit an order: from 207,932 to 6,917 in L1 gas. In Appendix~\ref{app:rollup}, the full interaction is shown in Figure~\ref{fig:lissyl2}, which illustrates how traders interact with \cm on Arbitrum including bridges, inboxes, sequencers and validators.

@@

In \cm, both the tokens and ETH that a trader wants to potentially use in the order book are preloaded into the contract. We discuss some alternative designs in Appendix~\ref{app:collateral}.

>>>>

We assume the reader is familiar with the following concepts: blockchain technology; smart contracts and decentralized applications (DApps) on Ethereum; how Ethereum transactions are structured, broadcast, and finalized; the gas model including the gas limit (approximately 11M gwei at the time of our experiments) per block. A \textbf{gas refund} is a more esoteric subject (not covered thoroughly in any academic work to our knowledge) that we use heavily in our optimizations. Briefly, certain EVM operations (\texttt{SELFDESTRUCT} and \texttt{SSTORE 0}) cost negative gas, with the follow caveats: the refund is capped at 50\% of the total gas cost of the transaction, and (2) the block gas limit applies to the pre-refunded amount (\ie a transaction receiving a full refund can cost up to 5.5M gas with an 11M limit). We provide full details of all of these topics in the full version~\cite{https://doi.org/10.48550/arxiv.2101.06291}.

@@

Table~\ref{tab:eval2} illustrates various trade execution systems and summarizes their advantages and disadvantages. A full justification for the table can be found in~\cite{https://doi.org/10.48550/arxiv.2101.06291}. Briefly, fully decentralized, on-chain exchanges require the lowest trust, provide instant settlement, and have transparent trading rules that will always execute correctly. Front-running attacks (see Section~\ref{sec:front} for a very thorough discussion) are weaknesses inherent in blockchains that require specific mitigation.

@@

A call market opens for traders to submit bids and asks which are enqueued until the market closes. Trades are executed by matching the best priced bid to the best priced ask until the best bid is less than the best ask, then all remaining trades are discarded. See~\cite{https://doi.org/10.48550/arxiv.2101.06291} for a numeric example. If Alice's bid of \$100 is executed against Bob's ask of \$90, Alice pays \$100, Bob receives \$90 and the \$10 difference (called a price improvement) is given to miners for reasons in explained in the front-running evaluation (Section~\ref{sec:front}).

@@

\item \textbf{Heap with Mapping.} In this variant, we store a key for the order in the heap instead of the entire order. Once a key is dequeued, the order struct is drawn from a Solidity mapping (which stores key-value pairs very efficiently). This is asymptotically the same and faster with variable-sized data.

@@

The lesson here is that gas refunds incentivize developers to clean up storage variables they will not use again, but it is highly contextual as to whether it will pay for itself. Further, the cap on the maximum refund means that refunds are not fully received for large cleanup operations (however removing the cap impacts the miners' incentives to include the transaction). We present a second case study of the cost-benefit of clearing a mapping when it is no longer needed (including our idea to store the mapping in its own contract so it can \texttt{SELFDESTRUCT} with a single function call) in~\cite{https://doi.org/10.48550/arxiv.2101.06291}. The unfortunate takeaway is, again, that it is cheapest to leave the mapping in place. Cleaning up EVM state is a complicated and under-explored area of Ethereum in the research literature. For our own work, we strive to be good citizens of Ethereum and clean up to the extent that we can---thus all PQs in Table~\ref{tab:PQUnitTests} implement some cleanup.

@@

\textit{Layer 2 (L2)} solutions~\cite{gudgeon2020sok} are a group of scaling technologies proposed to address specific drawbacks of executing transactions on Ethereum, which is considered \textit{Layer 1 (L1)}. Among these proposals, \textit{roll-ups} prioritize reducing gas costs (as opposed to other valid concerns like latency and throughput, which are secondary for \cm). We review two variants, \textit{optimistic roll-ups} and \textit{zk roll-ups}, in~\cite{https://doi.org/10.48550/arxiv.2101.06291}. Briefly, in a roll-up, every transaction is stored (but not executed) on Ethereum, then executed off-chain, and the independently verifiable result is pushed back to Ethereum, with some evidence of being executed correctly. We also compare \cm on Arbitrum to Loopring 3.0 in~\cite{https://doi.org/10.48550/arxiv.2101.06291}.

@@

In our \cm variant on Arbitrum, the validators do all computations (both enqueuing and dequeuing) so we choose to use a heap with dynamic array for our priority queue, which balances the expense of both operations. Heaps are 32\% more efficient than linked lists for submitting orders and 29\% less efficient for closing. Recall that without a roll-up, such a priority queue can only match 38 pairs at a cost of 5,372,679 gas. Table~\ref{tab:arbitrum_performance} shows that 38 pairs cost only 6,569 in L1 gas (a 99.88\% savings). This is the cost of submitting the \texttt{closeMarket()} transaction to the Inbox to be recorded, which is 103 bytes of calldata. Most importantly, recording \texttt{closeMarket()} in the Inbox will always cost around 6,569 even as the number of trades increases from 38 pairs to thousands or millions of pairs. Of course, as the number of trades increase, the work for the validators on L2 increases, as measured in ArbGas. The price of ArbGas in Gwei is not well established but is anticipated to be relatively cheap.  Arbitrum also reduces the costs for traders to submit an order: from 207,932 to 6,917 in L1 gas. We illustrate the interaction between the traders and \cm on Arbitrum including bridges, inboxes, sequencers and validators in~\cite{https://doi.org/10.48550/arxiv.2101.06291}.

@@

In \cm, both the tokens and ETH that a trader wants to potentially use in the order book are preloaded into the contract. We discuss some alternative designs in~\cite{https://doi.org/10.48550/arxiv.2101.06291}.
